Summer 2025 ToDo

### 2025-11-12 Relations/Paper/Summer_2025_TODO.tex
New definition layout. Typos fixed. Proper URLs
todo update

\section*{October 15th TODO / Oct 22nd}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item [\done] Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item [\done] Do we want to keep anything in the old/delete section of WF?
  \item [\done] Do we want to add anything about counter examples or positive examples? 
  \item [\done] We may want to use words rather than macros in certain locations
  \item [\done] Check through the comments in general in the section. 
\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
\item [\done] make the WF macro bold font?
\item add wfseq not not to the definitions?
\item [\done] Go through the bibliography links. Not all of them are currently working!
\item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
\item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
\item [\done] Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
\item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
\item [\done] Change the macro for FB so that it is also boldface
\item [\done, did SN to WN instead] update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
\item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
\end{todolist}

\section*{Plan for PLDI submission}
\begin{todolist}
\item[X] Aim for first draft finished by the end of the 29th.
\item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
\item [\done] discussion env has qed boxes which shouldn't be there.
\item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
\item Make consistent how we display definitions. 
\item [\done] Work on the conclusion
\item Need to fix how we put urls in for bibliography. Currently not quite working. 
\item Run through and compile everything, make sure we didn't introduce any bugs
\item Submit 
\item Add a paragraph or two giving a short overview/summary of Agda.
\item Go through the code, make naming consistent and self-documenting
\item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
\item Consider adding some more motivations 
\item Look at the seq-minus vs. seq-not-not issue 
\item Final read through (wed?)
\item Submission deadline is Thursday 13th 
\end{todolist}

>>>>

\section*{October 15th TODO / Oct 22nd}
\begin{todolist}     
  \item It's possible to have a term rewrite system with good properties like FB and the relation being decidable. But not satisfying accCor. That is something that can be added in a final touch of the paper. Either a remark or example, where a term rewrite system does not validate accCor. (In the lambda calculus, there are computable perpetual strategies. We think they're concerned with weak normalization. Not sure if it can be done with strong normalization.)
  \item [\done] Do a final read through of the information below the figure. Have we captured all the most important information / Are we repeating ourselves?
  \item [\done] Do we want to keep anything in the old/delete section of WF?
  \item [\done] Do we want to add anything about counter examples or positive examples? 
  \item [\done] We may want to use words rather than macros in certain locations
  \item [\done] Check through the comments in general in the section. 
\item [\done]  CHange WFseq not not to WFseq- in the macro. We are sticking with this for now. If we have time we can investigate the relation between the two.
\item [\done]  Make the diagram horizontal rather than vertical. Spoof it up and we can compare next week.
\item [\done]  Use of macros in WF section. Double check the right one is being used. Don't use the "is'' macro at all in this section. Be consistent on whether we are using macros. 
\item Does WFseq- with MP== imply WFseq? (W're thinking it will need rdec as well to give us the implication).
\item [\done] make the WF macro bold font?
\item add wfseq not not to the definitions?
\item [\done] Go through the bibliography links. Not all of them are currently working!
\item We want to start looking at examples. What we want to know is whether a first order rewrite system with some minimal properties implies some of our classical properties. E.g. lambda calculus satisfies some of our classical properties. As does first order term rewrite system. Follow up question: how big of an issue is it that accCor is not provable? Can we prove is isn't satisfied? 
\item [\done] Make a connection in the final WF section talking about how SN doesn't imply WN constructively. (we've started writing this sentence). 
\item [\done] We may need to add to the WFCounters file, if we have SN implies WN then every subset of the natural numbers is decidable.  
\item [\done] Make sure we have a proof of the implication from SN to WN given FB and decidability of a relation (to back up our claim in our introduction).
\item check TERESE and see first order term rewrite systems example which could be valid for showing classical and constructive formalization coincide. First order term rewrite systems are (always?) fb and R is dec. 
\item [\done] Change the macro for FB so that it is also boldface
\item [\done, did SN to WN instead] update wfcounters to show that asserting wfmin implies the excluded middle (and wfmindne the weak excluded middle).
\item [\done] In wfcounters we should have a system that is SN but not WN (WN implies excluded middle). 
\item make an external bibliography file rather than inlining in main file.
\end{todolist}

\section*{Plan for PLDI submission}
\begin{todolist}
\item[X] Aim for first draft finished by the end of the 29th.
\item[\done] Make a main file at this point to conform to this conference's style. Possibly a sub-folder for each conference.
\item [\done] discussion env has qed boxes which shouldn't be there.
\item[\done] from wellfounded extra move the implication of fb -> isdec -> isMinDec. move to implications. 
  Use this to take this SNdec→WN to have a full proof from fb, isdec, sn -> wn. (issue in moving to fb file due to reversal of relation direction!) 
\item Make consistent how we display definitions. \sacomment{I've made a change which I think looks better (bullet point style.) If we're happy with this change we can apply it to the wellfoundedness section too unless we rely on the numbering/reference the numbers}
\item [\done] Work on the conclusion
\item Need to fix how we put urls in for bibliography. Currently not quite working. \sacomment{Now all urls, if happy with how it looks we can tick it off. }
\item Check the PLDI page for submission rules/requirements. In particular the bibliography style 
\item Run through and compile everything, make sure we didn't introduce any bugs
\item Check the layout of figures through the paper. Counterexamples for example is currently `off'. 
\item Submit 
\item Add a paragraph or two giving a short overview/summary of Agda.
\item Go through the code, make naming consistent and self-documenting
\item Once we've got a current draft finished. Look in Teresa for first order term rewrite systems and see how many we can represent using our code.
\item Consider adding some more motivations 
\item Look at the seq-minus vs. seq-not-not issue 
\item Final read through (wed?)
\item Submission deadline is Thursday 13th 
\end{todolist}
